Summary of tumor cell classification with `SingleR` for `r params$library_id`

### 2024-07-24 analyses/cell-type-ewings/template_notebooks/auc-singler-workflow/02-singler-results.Rmd
move scripts and notebooks
add missing variable

# get the sum of expression of all genes for each cell type
gene_exp_df <- cell_types |>
  purrr::map(\(type){
    calculate_sum_markers(marker_genes_df, type)
  }) |>
  purrr::reduce(dplyr::inner_join, by = "barcodes")

@@

### Tumor cells annotated by `SingleR` and `AUCell`

>>>>

# get the sum of expression of all genes for each cell type
gene_exp_df <- cell_types |>
  purrr::map(\(type){
    calculate_sum_markers(marker_genes_df, sce, type)
  }) |>
  purrr::reduce(dplyr::inner_join, by = "barcodes")

@@

### Tumor cells annotatd by `SingleR` and `AUCell`
